Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2024-12-07 _tex/index.tex
Built site for gh-pages

\caption{\label{fig-dispersion}The effect of different dispersions
between stimuli on the distribution of the discriminal difference}

@@

\caption{\label{fig-correlation}The effect of correlation on the
distribution of the discriminal difference}

>>>>

\caption{\label{fig-dispersion}Discrepancies in the stimuli dispersions
and tehir effect on the distribution of the discriminal difference}

@@

\caption{\label{fig-correlation}The correlation between stimuli and its
effect on the distribution of the discriminal difference}
